Title

### 2017-03-25 paper.tex
adjust sd-heavy-d image size

    \begin{figure} \centering \includegraphics[width=3.5in]{img/sd-heavy-d.png} \caption{Scheduler duration distribution
    of cyclictest with heavy load} \label{fig:sd_heavy_d} \end{figure}

>>>>

    \begin{figure} \centering \includegraphics[width=3in]{img/sd-heavy-d.png} \caption{Scheduler duration distribution
    of cyclictest with heavy load} \label{fig:sd_heavy_d} \end{figure}
